%%%%%%%%% SEP Group 19 Meeting Week 4   %%%%%%%%%%
%%%%%%%%% Author: Yawen Luo  %%%%%%%%%%%%%%%%%
%%%%%%%%% 18 August 2015 %%%%%%%%%%%%%%%%%%


\documentclass[a4paper] {article}
\usepackage{array}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=3cm,bottom=4cm}
\pagestyle{empty}

\begin{document}
	
	\vspace*{-50pt}
	
	%%% time and location
	\noindent The \emph{second} Software Engineering Group \emph{19} Project \emph{status} meeting will
	be held in \textbf{Ingkarni Wardli Room 4.62} at \textbf {3:30pm} on \textbf{Monday 18 August 2015}.
	
	
	%%% title
	\begin{center}
		\huge \textbf {Agenda}
	\end{center}
	
	
	
	%%%% begin document
	\section*{Chair: Luo Yawen}
	
	\vspace*{10pt}
	
	%%% present
	\section{Present}
	\begin{itemize}
		\item a1657343 Luo Yawen (Documentation Team)
		\item a1662541 Yang Jiajun (Programming Team)
		\item a1653772 Yun Zhang (Project Manager)
		\item a1671836 Wei Jingwen (Programming Team)
		\item a1690773 Wang Yuzhu (Documentation Team)
		\item a1146944 Zander Shaun Nathan (Documentation Team)
	\end{itemize}
	
	%%% apologies
	\section{Absent with no Apologies}
	\begin{itemize}
		\item a1651541 Lee So Min
	\end{itemize}  
	
	%%% client
        \section{Client}
        \begin{itemize}
            \item \emph{MesaMap} Company
        \end{itemize} 
	
	%%% objectives
	\section{Objectives}
	\subsection{Requirement Elicitation}			
	Review the last meeting and if there are some unsure issues.
	
	\begin{enumerate}
	\item How do you define a no go zone? Colour? Shape?
	\item Is the communications tower and operation base considered as a single building?
	\item The robot need to work automatically, in what scenario does it need to work automatically?
	\item How many different types of area, and how does the robot detects the different areas? 
	\item After finishing the map, dose the robot need to tell itself the no-go zones or it's just controlled by us?
	\item If we lost communication between the robot and the operator, the robot should stop or go back?
	\item When will be a suitable DTD available?
	\item Dose the client provide a paper/card for representing of the terrain, or we construct it?
	\item What does the reference mean in the template of SPMP? Is it the normal reference?
	\item Will the base tower ever move? Will there only one?
	\item Are cliffs only on the external edge of the mesa?
	\item What is the communication way ? Wifi, or Bluetooth or cable?
	\item What is the effective distance range of the central control brick?
	\item For every single change in the procedure of the SEP, de we need to demonstrate it in documents or we just include the latest version?
\end{enumerate}
	
	\subsection{Milestone}
	The group starts to allocate whole tasks and prepares the initial milestone to negotiate.

	%%% other issues
	\section{Next Meeting}
	Note: Next meeting to be held at \textbf{3:30pm} on \textbf {25 August, 2015}. 
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	\\
	
	\begin{quote}
	         \centering
	         Milestone
         \end{quote}

         \begin{table} 
         \begin{tabular} 	
	         {|m{0.7cm}|m{12.6cm}|m{2.7cm}|}
	         \hline
	         \textbf{No.} & \textbf{Planned Features} & \textbf{Features Demonstrated (tick if same)}\\
	         \hline
	         1 & Finish Software Requirements Specification (SRS) 1st Draft - week 5 & \\ [3.5ex]
	         \hline
	         2 & Robot Movement Demo - week 6 & \\[3.5ex]
	         \hline
	         3 & SRS feedback negotiation - week 6 & \\[3.5ex]
	         \hline
	         4 & Finish Software Engineering and Project Software Project Management Plan (SPMP) 1st Draft - week 7 & \\[3.5ex]
	         \hline
	         5 & Finish Software Design Document (SDD) 1st Draft - week 8 & \\[3.5ex]
	         \hline
	         6 & SPMP feedback negotiation - week 8& \\[3.5ex]
	         \hline
	         7 & Robot Movement - week 9 & \\[3.5ex]
	         \hline
	         8 & Software test - week 9 & \\[3.5ex]
	         \hline
	         9 & Testing report - week 9 & \\[3.5ex]
	         \hline
	         10 & SDD feedback negotiation - week 10 & \\[3.5ex]
	         \hline
	         11 & Finish user manual - week 11 & \\[3.5ex]
	         \hline
	         12 & Submit final draft - week 12 & \\[3.5ex]
	         \hline
	         13 & Final project presentation - week 13 & \\[3.5ex]
	         \hline
         \end{tabular}
         %\end{table}

         %\begin{table}	
         \vspace{1cm}
         \textbf{Signature:}\\
         \begin{tabular} 
	          {|p{3.9cm}|p{3.9cm}|p{3.9cm}|p{3.9cm}|}
	         \hline
	          &  & & \\ [3.5ex]
	         \hline
	         & & & \\ [3.5ex]
	         \hline
         \end{tabular}
         \end{table}
	


	
\end{document}


	
