\documentclass[a4paper]{article}
\title{Minutes of Meeting}
\author{Group PG 19}
\date{12 August, 2015}

\begin{document}
\maketitle
\section*{Attendance}
\begin{tabular}{l l}
\textbf{Chair:} &a1653772 Zhang Yun\\
\textbf{Secretary:}&a1446944 Shaun Zander\\
&a1653772 Zhang Yun\\
&a1662541 Yang Jiajun\\
&a1653772 Zhang Yun\\
&a1671836 Wei Jingwen\\
&a1690773 Wang Yuzhu\\
\textbf{Absent:}&a1651541 Lee So Min (no apologies)
\end{tabular}

\section{Time and Place}
The first Software Engineering Group 19 Project status meeting will be held in SEP Lab at 3:30pm on Tuesday, 11th Aug 2015.

\section{Quorum Announcements}
The Chairman announced that a quorum of the group was present, and that the meeting, having been duly convened, was ready to proceed with its business

\section{Introduction to the Project}
The Client gave a short summary of the project to be undertaken. Group will be provided with a robot that will be tasked with navigating a terrain and plotting a map of that terrain.

\section{Requirements Elicitation}

\subsection{Overview}
The meeting chair explained that there was a number of questions that were needed to be asked to the client necessary for gathering requirements for the project.

\subsection{Feedback from Questions}
\begin{enumerate}
\item Our top priority is to currently deal with the mapping\item The robot shall detect when it can not go into a no go zone - specified by the client - Will need to be a requirement.\item The robot shall know where it is in real time - specified by the client - Will need to be a requirement.\item The robot shall be aware of the terrain - specified by the client - More information is required before this can become a requirement.\item The robot shall not collide into objects and need to avoid obstacles - specified by the client - Will need to be a requirement.\item The robot shall not travel at an excessive speed - specified by the client - Research will need to be undertaken to be able to quantify what an accept- able speed limit is before this can become a requirement.\item The system shall need to map the coloured circles. The client does not know what the circles are currently used for however it is essential that they are mapped.\item There shall be a recovery system for when the link is broken with the robot - specified by the client - Will need to be a requirement however more research and information will be required before this can be planned.\item The top priority of the system is safety followed by the completeness of the mapping. Reliability of the task is of concern rather than the speed of the task.\item The robot shall not fall off of any ledges - specified by the client - Will need to be a requirement.\item The robot shall only report only to the limits it can physically map based on the size constraints and practicalities of the robot - specified by the client - Will need to be a requirement.\item There will only be one robot doing the mapping task. Therefore the system shall be designed with that in mind.\item The robot must be aware of its power resources and be able to return to its starting location when sent to plot a map - specified by the client - Research will need to be required for this to become a requirement.
   \end{enumerate}

\section{Next Meeting}
The next client meeting will be held at \textbf{3:30pm} in the \textbf{11th of August, 2015.} It will be held in the \textbf{SEP Lab}.

\end{document}