%%%%%%%%% SEP Group 19 Meeting Week 3   %%%%%%%%%%
%%%%%%%%% Author: Yun Zhang%%%%%%%%%%%%%%%%%
%%%%%%%%% 11 August 2015 %%%%%%%%%%%%%%%%%%


\documentclass[a4paper] {article}
\usepackage{array}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=3cm,bottom=4cm}
\pagestyle{empty}

\begin{document}
	
	\vspace*{-50pt}
	
	%%% time and location
	\noindent The \emph{second} Software Engineering Group \emph{19} Project \emph{status} meeting will
	be held in \textbf{Ingkarni Wardli Room 4.62} at \textbf {3:30pm} on \textbf{Monday 11 August 2015}.
	
	
	%%% title
	\begin{center}
		\huge \textbf {Agenda}
	\end{center}
	
	
	
	%%%% begin document
	\section*{Chair: Zhang Yun}
	
	\vspace*{10pt}
	
	%%% present
	\section{Present}
	\begin{itemize}
		\item a1657343 Luo Yawen (Documentation Team)
		\item a1662541 Yang Jiajun (Programming Team)
		\item a1653772 Yun Zhang (Project Manager)
		\item a1671836 Wei Jingwen (Programming Team)
		\item a1690773 Wang Yuzhu (Documentation Team)
		\item a1146944 Zander Shaun Nathan (Documentation Team)
	\end{itemize}
	
	%%% apologies
	\section{Absent with no Apologies}
	\begin{itemize}
		\item a1651541 Lee So Min
	\end{itemize}  
	
	%%% client
        \section{Client}
        \begin{itemize}
            \item \emph{MesaMap} Company
        \end{itemize} 
	
	%%% objectives
	\section{Meeting Content}
	The group shall highlight and clarify with the lecturer on the following items:
	\subsection{Introduction}			
	The chair introduces the team to the client.
	\subsection{Requirement Elicitation}
	The chair shall clarify on the following subsections of the Supporting Plan in the report:
	\begin{enumerate}
	\item When will DTD be given? Should XML file be checked against this DTD?
	\item How should NGZ be specified by operators? Via coordinates, shape?
	\item What factors should be taken into account concerning safety of the robots?
	\item What assistance should provided to the operators while they are operat- ing the robot? Obstacle?
	\item Should be the binary code counted in the reused percentage of the project?
	\item What is the purpose of some colour circles on the boundary at unspecified points?
	\item Does the robot keep its trace of exploration? How long?
	\item Do need a server to support the robot and daily operation?
	\item What is the working environment?
	\item How long will the robot work per day?
	\item Because the robot needs to be charged, do we need to more than one robot?
\end{enumerate}
	\subsection{Requirement Confirmation}
	The chair shall clarify on the viewing and concepts, which was discussed during the meeting.

	%%% other issues
	\section{Next Meeting}
	Note: Next meeting to be held at \textbf{3:30pm} on \textbf {18 August, 2015}. 
	
\end{document}


	
