%%%%%%%%% SEP Group 19 Meeting Week 5   %%%%%%%%%%
%%%%%%%%% Author: Wang Yuzhu%%%%%%%%%%%%%%%%%
%%%%%%%%% 52 August 2015 %%%%%%%%%%%%%%%%%%


\documentclass[a4paper] {article}
\usepackage{array}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=3cm,bottom=4cm}
\pagestyle{empty}

\begin{document}
	
	\vspace*{-50pt}
	
	%%% time and location
	\noindent The \emph{third} Software Engineering Group \emph{19} Project \emph{status} meeting will
	be held in \textbf{Ingkarni Wardli Room 4.62} at \textbf {3:30pm} on \textbf{Tuesday 25 August 2015}.
	
	
	%%% title
	\begin{center}
		\huge \textbf {Agenda}
	\end{center}
	

	%%%% begin document
	\section*{Chair: Wang Yuzhu}
	
	\vspace*{10pt}
	
	%%% present
	\section{Present}
	\begin{itemize}
		\item a1657343 Luo Yawen (Documentation Team)
		\item a1662541 Yang Jiajun (Programming Team)
		\item a1653772 Zhang Yun (Project Manager)
		\item a1671836 Wei Jingwen (Programming Team)
		\item a1690773 Wang Yuzhu (Documentation Team)
		\item a1146944 Zander Shaun Nathan (Documentation Team)
	\end{itemize}
	
	%%% apologies
	\section{Absent with no Apologies}
	\begin{itemize}
		\item a1651541 Lee So Min
	\end{itemize}  
	
	%%% client
        \section{Client}
        \begin{itemize}
            \item \emph{MesaMap} Company
        \end{itemize} 
	
	%%% objectives
	\section{Meeting Content}
	The group shall highlight and clarify with the client on the following items:
	
	\subsection{Poster Presentation}
	The chair introduces the poster to the client.
	
	\subsection{GUI-Prototype}
	The chair shall clarify on the following subsections of the Supporting Plan in the report:

	\subsubsection{Start Screen}
	\begin{enumerate}
	        \item What is the information should be displayed on the information area?
	        \item Do the start button need a alert message when a user push it?
	        \item Do the exit button need a alert message when a user push it?
   \end{enumerate}
   
	\subsubsection{Main Screen}
	\begin{enumerate}
	        \item Do the screen need to tell the user the position of the robot? By longitude and latitude or the distance between the base station and the robot?
	        \item What are the error messages and information do the robot need to convey to the user?
	        \item Do the battery need to be displayed as the percentage type?
	        \item Do the battery need to a alarm when the remaining battery is below 1/4 (25\%)?
	        \item Do the screen need an auto button?
	        \item Can the NGZ be cleared in main screen or only in the NGZ set screen?
			\item Do we need another screen to load and save the map?
			\item Do the screen need an ’return to base’ button?
			\item Do the energy button need a alert message when a user push it?
			\item Do we need a help button to provide the help information to the user?
			\item When the user push the exit button, what should the robot do?
			\item Do the exit button need a alert message when a user push it?
   \end{enumerate}
   
	\subsubsection{NGZ set Screen}
	\begin{enumerate}
	        \item Do the map need to display coloured circles?
	        \item Do the NGZ need a colour set button?
	        \item Do this screen need an exit button?
	        \item Do the system need the NGZ set screen? or match this into the main screen?
   \end{enumerate}
   
	\subsubsection{General}
	\begin{enumerate}
	        \item Do we need any other button on these screen?
	        \item Do we need to change the design e.g. colour and the position of the screen?
	        \item Do you have any other idea or advise about the screen?
   \end{enumerate}
   
   \subsection{Milestone}
	\begin{enumerate}
		\item Have finished the SRS 1st Draft in last week (week 4) and submitted the document.
		\item Working on the robot design and movement.
		\item Next week(week 6) we will update the SRS according to the feedback from week 6.
   \end{enumerate}
   
   \subsection{Requirement Confirmation}
	The chair shall clarify on the viewing and concepts, which was discussed during the meeting.
   
	%%% other issues
	\section{Next Meeting}
	Note: Next meeting to be held at \textbf{3:30pm} on \textbf {1 September, 2015}. 
	
\end{document}


	
