\documentclass[a4paper]{article}
\title{Minutes of Meeting}
\author{Group PG 19}
\date{20 October, 2015}

\begin{document}
\maketitle
\section*{Attendance}
\begin{tabular}{l l}
\textbf{Chair:} 
&a1662541 Yang Jiajun\\
\textbf{Secretary:}&a1690773 Wang Yuzhu\\
&a1662541 Yang Jiajun\\
&a1657343 Luo Yawen\\
&a1653772 Zhang Yun\\
&aa1653772 Zhang Yun\\
\textbf{Absent:}&a1651541 Lee So Min (no apologies)\\ &a1446944 Shaun Zander(no apologies)
\end{tabular}

\section{SDD Crtique}
The document is well structured and flows well. It is for the most part well laid out and easy to read.\\
\\
All elements of design are present, with some level of description.\\
\\
The primary diagram about system design, figure 1, is however not very clear. It is not just a software system -- it has hardware elements as well. Accordingly, the correspondence of sub-systems with hardware entities is not clear. One system component is not described in the text.\\
\\
More detail is needed to be an adequate design document. For example, "this component will need order information from communication component" is a very imprecise statement and does not provide much
assistance to an implementation team (for which this document is intended).\\\
\\
What notation is in use for the data descriptions? This section needs a lot more discussion connecting the various parts and explaining what the diagrams are for. How do the data items mentioned fit with system operations?\\
\\
Section 5 shows the beginnings of some useful information, but is not organised, and is very incomplete. Remember the SDD will be taken by an implementation team and used to build a system. Put yourselves in the position of that team, and read the document from their perspective. Could they do it?\\
\\
Section 6 is a good overview and conveys many essential elements, but more is needed.\\

\section{Mystery presentation}
Each member had a presentation of the role they choose.\\

\section{Next Meeting}
The next client meeting will be held at \textbf{1:00 pm} on the \textbf{03rd of November, 2015.} It will be held in the \textbf{SEP Lab}.

\end{document}