\documentclass[a4paper]{article}
\title{Minutes of Meeting}
\author{Group PG 19}
\date{6 October, 2015}

\begin{document}
\maketitle
\section*{Attendance}
\begin{tabular}{l l}
\textbf{Chair:} 
&a1653772 Zhang Yun\\
\textbf{Secretary:}&a1690773 Wang Yuzhu\\
&a1662541 Yang Jiajun\\
&a1657343 Luo Yawen\\
&a1653772 Zhang Yun\\
&a1671836 Wei Jingwen\\
\textbf{Absent:}&a1651541 Lee So Min (no apologies)\\ &a1446944 Shaun Zander(no apologies)
\end{tabular}

\section{SPMP Critique}
The following feedback was given for the SPMP Draft.
\begin{itemize}
	\item Well formatted and clearly organised.
	\item The evolution section is interesting, but give more insight into reasons.
	\item Refs and definitions need more detail.
	\item Section 4 write a narrative, not notes.
	\item Section 5 needs an introduction and much more explanation. This is a very important section, and you have given it vastly insufficient attention.
	\item Workplan is quite good, but milestones are indequately described.
	\item Configuration management is a good start. Say something about use of trunk, tags, branches..
	\item Document section is OK, but be more precise about process
	\item QA plan is superficial.
	
\end{itemize}
The mark for the SPMP Draft is a 11/20. Overall, this is disappointing compared to your previous efforts..


\section{Milestone1}
The following items were finished.
\begin{itemize}
	\item Robot Movement - Forward Back Left and Right
	\item Colour and distance sensor
	\item GUI Prototype
	\item Software Design Document (SDD) Draft
	\item Software Project Management Plan (SPMP) Draft
\end{itemize}

\section{Next Meeting}
The next client meeting will be held at \textbf{3:30pm} on the \textbf{13th of October, 2015.} It will be held in the \textbf{SEP Lab}.

\end{document}