%%%%%%%%% SEP Group 19 Meeting Week 5   %%%%%%%%%%
%%%%%%%%% Author: Jingwen Wei%%%%%%%%%%%%%%%%%
%%%%%%%%% 1 September 2015 %%%%%%%%%%%%%%%%%%


\documentclass[a4paper] {article}
\usepackage{array}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=3cm,bottom=4cm}
\pagestyle{empty}

\begin{document}
	
	\vspace*{-50pt}
	
	%%% time and location
	\noindent The \emph{forth} Software Engineering Group \emph{19} Project \emph{status} meeting will
	be held in \textbf{Ingkarni Wardli Room 4.62} at \textbf {3:30pm} on \textbf{Tuesday 1 September 2015}.
	
	
	%%% title
	\begin{center}
		\huge \textbf {Agenda}
	\end{center}
	

	%%%% begin document
	\section*{Chair: Wei Jingwen}
	
	\vspace*{10pt}
	
	%%% present
	\section{Present}
	\begin{itemize}
		\item a1657343 Luo Yawen (Documentation Team)
		\item a1662541 Yang Jiajun (Programming Team)
		\item a1653772 Zhang Yun (Project Manager)
		\item a1671836 Wei Jingwen (Programming Team)
		\item a1690773 Wang Yuzhu (Documentation Team)
		\item a1146944 Zander Shaun Nathan (Documentation Team)
	\end{itemize}
	
	%%% apologies
	\section{Absent with no Apologies}
	\begin{itemize}
		\item a1651541 Lee So Min
	\end{itemize}  
	
	%%% client
        \section{Client}
        \begin{itemize}
            \item \emph{MesaMap} Company
        \end{itemize} 
	
	%%% objectives
	\section{Meeting Content}
	The group shall highlight and clarify with the client on the following items:
	
	\subsection{Robot Movement Demo}
   
   % \subsection{Risk Management}
	%\begin{enumerate}
	%\item Human behaviour.
	%\item Technology and technical issues.
	%\item Hardware issues.
	%\item Late delivery of software.
	%\item Requirements change.
   %\end{enumerate}
	
	\subsection{SRS Critique}
	\begin{enumerate}
	        \item Should use case diagram included in the SRS?
	        \item Except the robot operator, is there any other worker or external system using this system?
	        \item Does communication between robot and control center need to be encrypted?
	        \item Is there any requirement about performance requirement about the robot exploring the map? e.g, How long at maximum does it take the robot to finish exploration? How far does the robot travel before completing its exploration task?
	        \item Should data be cached in the robot? If so, how long should it save the data? 
	        \item Should warnings such as low battery level be raised? If so, how to deliver them to users? Is it all right that the control center just show them on the GUI?
	        \item For priority of each requirement, do we need to describe and explain priorities specifically?
	        \item Do we need to add the anticipated achievement and error encountered? If so, in which part?
	        \item Can we implement some features that are not requested by the customer?
	        \item Should we use like use case, mode of operation, user class, object class and functional hierarchy in each system feature, or just one in one feature?
   \end{enumerate}
   
	%%% other issues
	\section{Next Meeting}
	Note: Next meeting to be held at \textbf{3:30pm} on \textbf {8 September, 2015}. 
	
\end{document}


	
