\documentclass[a4paper]{article}
\title{Minutes of Meeting}
\author{Group UG 19}
\date{1 September, 2015}

\begin{document}
\maketitle
\section*{Attendance}
\begin{tabular}{l l}
\textbf{Chair:} 
&a1671836 Wei Jingwen\\
\textbf{Secretary:}&a1446944 Shaun Zander\\
&a1690773 Wang Yuzhu\\
&a1653772 Zhang Yun\\
&a1657343 Luo Yawen\\
&a1662541 Yang Jiajun\\
&a1653772 Zhang Yun\\
\textbf{Absent:}&a1651541 Lee So Min (no apologies)
\end{tabular}

\section{Robot Movement Demo}
A demonstration was given of the robot showing the features of the robot and movement of the robot. An explanation of the known challenges was also given.\\
\\
The group asked what the surface of the map would be. MesaMap explained that the map would be paper laid on a solid table rather than on carpet.

\section{SRS Critique}
\subsection{Should use case diagrams be included in the SRS?}
Some us of use cases would be appropriate but not too much. You can use Use Case diagrams to communicate things that are important about the system so that it could be interesting for somebody reading it.

\subsection{Except the robot operator, is there any other workers or external systems using this system?}
No. Other entities that may involved are not of our concern.

\subsection{Does communication between robot and control centre need to be encrypted?}
It does not need to be encrypted. It is of secondary performance.

\subsection{Are there any performance requirements about the robot exploring the map to do with distance or time?}
There are no requirements regarding how long it should take or how far the robot should travel. The top priorities are safety and accuracy.

\subsection{Should data be cached in the robot? If so, how long should it save the data?}
That should be decided from the point of view of delivering the functionality of what they are expecting.

\subsection{For priority of each requirement, do we need to describe and explain priorities specifically?}
Yes, it is important. How you set the priorities are up to you but make sure they are consistent.

\subsection{Do we need to record any errors encountered? If so, in which part?}
MesaMap are unsure if this is required.

\subsection{Can we implement some features that are not requested by the customer?}
MesaMap would only like what is outlined in the requirements and not be surprised with any extra features. The client would need to agree on any requirements or features.

\subsection{Should we use Use Cases, modes of operation, user classes, object classes and functional hierarchy in each system feature, or just one in one feature?}
This is out of the knowledge domain of the client. How the system is implemented is up to the group provided that it meets how the architecture was outlined in the documentation.

\section{Next Meeting}
The next client meeting will be held at \textbf{3:30pm} on the \textbf{8th of September, 2015.} It will be held in the \textbf{SEP Lab}.

\end{document}