
\documentclass[a4paper] {article}
\usepackage{array}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=3cm,bottom=4cm}
\pagestyle{empty}

\begin{document}
	
	\vspace*{-50pt}
	
	%%% time and location
	\noindent The \emph{sixth} Software Engineering Group \emph{19} Project \emph{status} meeting will
	be held in \textbf{Ingkarni Wardli Room 4.62} at \textbf {3:30pm} on \textbf{Tuesday 15 September 2015}.
	
	
	%%% title
	\begin{center}
		\huge \textbf {Agenda}
	\end{center}
	

	%%%% begin document
	\section*{Chair: Shaun Zander}
	
	\vspace*{10pt}
	
	%%% present
	\section{Present}
	\begin{itemize}
		\item a1657343 Luo Yawen (Documentation Team)
		\item a1662541 Yang Jiajun (Programming Team)
		\item a1653772 Zhang Yun (Project Manager)
		\item a1671836 Wei Jingwen (Programming Team)
		\item a1690773 Wang Yuzhu (Documentation Team)
		\item a1146944 Zander Shaun Nathan (Documentation Team)
	\end{itemize}
	
	%%% apologies
	\section{Absent with no Apologies}
	\begin{itemize}
		\item a1651541 Lee So Min
	\end{itemize}  
	
	%%% client
        \section{Client}
        \begin{itemize}
            \item \emph{MesaMap} Company
        \end{itemize} 
        
	\section{Meeting Content}
	The group shall highlight and clarify with the client on the following items:
	
	\subsection{Review of previous minutes}
   	The chair will give a brief review of the last minutes.
	
	\subsection{GUI Demo}
	The group will showing a mock demonstration of the GUI on a computer. The purpose being to show how it will work on hardware. This may not be integrated with the robot yet.
   
    \subsection{Map Clarification}
    \begin{enumerate}
            \item Will the initial home coordinates be known as well as which direction is north?
            \item How big will the circles be?
            \item What colours other than red, yellow blue and green would we need to detect?
            \item What form will the home base take?
            \item Are there any errors of our terrain that need correcting?
        \end{enumerate}
     \subsection{Milestone Freeze - Week 10}
     We will be outlining our milestone deliverables fort week 10.
     
     \subsection{Mid-semester Break}
     We will be outlining the tasks that we will be working on over the mid-semester break.
     
     \subsection{Any Other Business}
     Anything else that was not outlined in this Agenda can be raised here.
	\section{Next Meeting}
	Note: Next meeting to be held at \textbf{3:30pm} on \textbf {6 October, 2015}. 
	
\end{document}


	
