\documentclass[a4paper]{article}
\title{Minutes of Meeting}
\author{Group PG 19}
\date{8 September, 2015}

\begin{document}
\maketitle
\section*{Attendance}
\begin{tabular}{l l}
\textbf{Chair:} 
&a1662541 Yang Jiajun\\
\textbf{Secretary:}&a1446944 Shaun Zander\\
&a1653772 Zhang Yun\\
&a1657343 Luo Yawen\\
&a1653772 Zhang Yun\\
&a1671836 Wei Jingwen\\
&a1690773 Wang Yuzhu\\
\textbf{Absent:}&a1651541 Lee So Min (no apologies)
\end{tabular}

\section{Review of the Last Minutes}
A summary of the previous meeting was presented. This included the robot movement demo and some questions of the SRS.

\section{SRS Critique}
The following feedback was given for the SRS Draft.
\begin{itemize}
	\item Header and Content - It contains good structure and content.
	\item Make sure to include the Group Name which is currently missing from the document.
	\item The document reads and flows well.
	\item Section 1 was a good statement of purpose and scope.
	\item Section 2 was well structured. However, a lot would be better with more detail and explanation. It would also benefit from having more non-technical information. This needs to be there for the client.
	\item Section 2.2 will need to be redone to explain it better. This is the best place for non-technical information.
	\item Section 2.3 needs better organisation and flow. It it good but does need more development.
	\item Section 3 needs to start with an introduction to explain what you are doing. Overall the requrements were good but need more development.
	\item The document had good numbering and formatting. Go through the template because it had what t put where such as acceptance criteria and dependencies.
	\item Section 4 needs more information but is very good.
	\item Section 5 has good diagrams and discussion. It is done well.
	\item Section 6 is also done well.
	\item Overall, it is done very well with good thinking and good foundation.
\end{itemize}
The mark for the SRS Draft is a 16/20. The average is 12/20 so this is a good submission.


\section{GUI Revision}
The revised GUI is an improvement on the last one. It is a lot clearer. However it is important that the GUI be presented in a workable form on a PC at this stage. A demo of the GUI will be presented in the client meeting of week 8.

\section {Week 9 Milestone Freeze}
The following was presented to be our Milestone Deliverables in week 9.

\begin{itemize}
	\item Robot Movement - Forward Back Left and Right
	\item Colour and distance sensor
	\item GUI Prototype
	\item Software Design Document (SDD) Draft
	\item Software Project Management Plan (SPMP) Draft
\end{itemize}

\section{Next Meeting}
The next client meeting will be held at \textbf{3:30pm} on the \textbf{15th of September, 2015.} It will be held in the \textbf{SEP Lab}.

\end{document}